Pool Model

### 2025-08-28 pool_model.tex
rename variable
write short description of abm formulation

        \dot{L_A} = -\lambda_A R^* L_A\\
        \dot{G_A} = \lambda_A R^* L_A + \alpha_A R^* G_A\\
        \dot{L_B} = -\lambda_B R^* L_B\\
        \dot{G_B} = \lambda_B R^* L_B + \frac{\alpha_B}{1 + \mu_I I} R^* G_B\\

@@

        \dot{R^*} = -\frac{\alpha_A}{G_\text{max}} R^* G_A-\frac{\alpha_B}{(1 + \mu_I I) G_\text{max}} R^* G_B \\

@@

% ------------------------------------------------------------------------------------------------
\subsection{Constructing an Agent-Based Pool Model}
We use \texttt{cellular\_raza}~\cite{Pleyer2025} to implement an \ac{abm}.

@@

    \dot{L_A} &= -\lambda_A R^* L_A\\
    \dot{G_A} &= \lambda_A R^* L_A + \alpha_A R^* G_A\\
    \dot{L_B} &= -\lambda_B R^* L_B\\
    \dot{G_B} &= \lambda_B R^* L_B + \frac{\alpha_B}{1 + \mu_I I} R^* G_B\\
    \dot{R^*} &= -\frac{\alpha_A}{G_\text{max}} R^* G_A-\frac{\alpha_B}{(1 + \mu_I I) G_\text{max}} R^* G_B \\

@@

        \multirow{2}{*}{Resource}
        & \multirow{2}{*}{$\displaystyle \dot{R^*} = - \frac{\alpha}{(1 + \mu_I I) G_\text{max}} R^* G$}
        & \multirow{2}{*}{$\displaystyle \dot{R} = -\frac{u}{1+\nu_I V_D^{-1}I} \frac{1}{V_D} R V$}
        & $\displaystyle G_\text{max} = [R_0] V_D \sigma$\\

@@

        Volume
        & $\displaystyle \dot{G} = \frac{\alpha}{1 + \mu_I I} R^* G$
        & $\displaystyle \dot{V} = \frac{u}{1+\nu_I V_D^{-1} I} \frac{1}{V_D}\sigma R V$
        & $\displaystyle \alpha = u[R_0]\sigma$\\

@@

        Total volume                & $G_\text{max}$& $2.0\cdot 10^5$\unit{\micro\metre\cubed}

@@

        Relative Nutrients          & $R^*$         & $1.0$

>>>>

        \dot{L_A} = -\lambda_A R L_A\\
        \dot{G_A} = \lambda_A R L_A + \alpha_A R G_A\\
        \dot{L_B} = -\lambda_B R L_B\\
        \dot{G_B} = \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B\\

@@

        \dot{R} = -\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R G_B \\

@@

% ------------------------------------------------------------------------------------------------
\subsection{Constructing an Agent-Based Pool Model}
The previously considered \ac{ode} formulation makes extensive use of the assumption that the
bacteria are evenly distributed and all communications and interactions between bacteria or
nutrients occurr on time scales much faster than the remaining processes.
However, for heterogenous systems or nutrients with low diffusability, this assumption might not be
valid.\\
In order to construct a model which can encapsulate diffusion of nutrients and heterogeneity of
the bacteria or nutrients, we have to take into consideration the spatial component of our setup.
\acp{abm} force researchers to think in terms of cellular processes, thus bridging the gap from a
collective (bulk) model to an individual-based (single-cell) description.
The following sections will demonstrate how a given \ac{ode} system can be translated into a
custom-built \ac{abm} which has only a few more overall parameters.
To construct our \ac{abm}, we use \texttt{cellular\_raza}~\cite{Pleyer2025} which was designed to
provide maximal flexibility for researchers in order to construct minimalist models.
Without the ability to define and control the precise behavior of our cell-agents, the following
approaches would not be possible.

@@

    \dot{L_A} &= -\lambda_A R L_A\\
    \dot{G_A} &= \lambda_A R L_A + \alpha_A R G_A\\
    \dot{L_B} &= -\lambda_B R L_B\\
    \dot{G_B} &= \lambda_B R L_B + \frac{\alpha_B}{1 + \mu_I I} R G_B\\
    \dot{R} &= -\frac{\alpha_A}{N_t} R G_A-\frac{\alpha_B}{(1 + \mu_I I) N_t} R G_B \\

@@

        \multirow{2}{*}{Resource}
        & \multirow{2}{*}{$\displaystyle \dot{R} = - \frac{\alpha}{(1 + \mu_I I) N_t} R G$}
        & \multirow{2}{*}{$\displaystyle \dot{R} = -\frac{u}{1+\nu_I V_D^{-1}I} \frac{1}{V_D} R V$}
        & $\displaystyle N_t = [R_0] V_D \sigma$\\

@@

        Volume
        & $\displaystyle \dot{G} = \frac{\alpha}{1 + \mu_I I} R G$
        & $\displaystyle \dot{V} = \frac{u}{1+\nu_I V_D^{-1} I} \frac{1}{V_D}\sigma R V$
        & $\displaystyle \alpha = u[R_0]\sigma$\\

@@

        Total volume                & $N_t$& $2.0\cdot 10^5$\unit{\micro\metre\cubed}

@@

        Relative Nutrients          & $R$         & $1.0$
